MSE 327 Project

### 2020-11-18 MSE327/EDA_outcome.Rmd
saving the plot in a nice format

plot1 <- ggplot(df, aes(pmfu, color = Area, fill = Area)) +
  geom_histogram(aes(y=..density..), position="identity", alpha=0.5, bins = 25) +
  geom_density(alpha = 0.25) +
  theme_minimal() + 
  ggtitle("Outcome: Ambient PM2.5 2010-2012") +
  xlab("Ambient PM2.5 2010/12")
```

@@

plot2 <- ggplot(df_1, aes(pmbase2002_2004, color = Area, fill = Area)) +
  geom_histogram(aes(y=..density..), position="identity", alpha=0.5, bins = 25) +
  geom_density(alpha = 0.25) +
  theme_minimal() + 
  ggtitle("Outcome: Ambient PM2.5 2002-2004") + 
  xlab("Ambient PM2.5 2002/04")
```

@@

```{r}
par(mfrow = c(2, 2))
plot1
plot2
plot3
```

>>>>

plot1 <- ggplot(df, aes(pmfu, color = Area, fill = Area)) +
  geom_histogram(aes(y=..density..), position="identity", alpha=0.5, bins = 25) +
  geom_density(alpha = 0.25) +
  theme_minimal() + 
  theme(legend.position = "none") +
  ggtitle("Outcome: Ambient PM2.5 2010-2012") +
  xlab("Ambient PM2.5 2010/12")
```

@@

plot2 <- ggplot(df_1, aes(pmbase2002_2004, color = Area, fill = Area)) +
  geom_histogram(aes(y=..density..), position="identity", alpha=0.5, bins = 25) +
  geom_density(alpha = 0.25) +
  theme_minimal() + 
  theme(legend.position = "none") +
  ggtitle("Outcome: Ambient PM2.5 2002-2004") + 
  xlab("Ambient PM2.5 2002/04")
```

@@

```{r}
library("gridExtra")
lay <- rbind(c(1,2),
             c(3,3))
all_plots <- grid.arrange(plot2, plot1, plot3, layout_matrix = lay)
#grid.arrange(plot1, plot2, plot3, ncol = 2, nrow = 2)

ggsave(
  "hist_figure1.png",
  plot = all_plots,
  width = 7.5,
  height = 4,
  dpi = 1200
)
```
